\documentclass{article}[12pt]

\usepackage{hyperref}

\title{Individual Project Report}
\author{Pedro Uria Rodriguez}

\begin{document}

\maketitle

\section*{Individual Work}

\begin{itemize}
\item Researched on the topic, mainly by reading \href{https://arxiv.org/abs/1709.01620}{this great source}.
\item Came up with the network architecture, training and generator functions.
\item Wrote all the code located in the main \texttt{code} file apart from \texttt{combine.py}. 
\item Helped write and revise the project proposal.
\item Wrote the \textit{Encoding}, \textit{Network Architecture}, \textit{Training}, \textit{Generator} sections on the project report. TODO
\item Designed the slides in LaTeX and filled up the TODO sections ... 
\item Experimented with the networks and generated some music, located in \texttt{results} as well as on the main \texttt{generated-music} folder.
\item Organized the repo and documented most TODO of the \texttt{README.md} files.

\end{itemize}

\section*{Percentage of non-self written code}

\begin{itemize}

\item \texttt{Data\_Preprocessing.ipynb}: 0\%. I referred to the \texttt{music21} \href{https://web.mit.edu/music21/doc/}{documentation}, but I did not copy any code as it was in there, just played with my own cases and with what was relevant for the project.
\item \texttt{encoder\_decoder.py}: 0\%.
\item \texttt{eval\_processor.py}: 0\%
\item \texttt{multi\_many\_hot\_encoder\_decoder.py}: 0\%
\item \texttt{training\_many\_deff.py}: 2.4\%. I used  \href{https://stackoverflow.com/questions/973473/getting-a-list-of-all-subdirectories-in-the-current-directory}{this} to walk the data/classical subdirectory, and followed \href{https://github.com/amir-jafari/Deep-Learning/blob/master/Pytorch_/7-RNN/1_RNN.py}{this} for the general structure of the architecture and training code, although heavily modified.
\item The rest of the scripts would be the same as this last one, so about the same percentage. 

\end{itemize}

\end{document}